QALY Comparisons - `r params$experiment` - `r params$intervention` - `r params$baseline`

### 2024-03-12 minos/outcomes/QALY_comparison2.Rmd
Refactored QALY_comparison2.Rmd to accept multiple interventions and visualise them together

```{r}
experiment <- params$experiment
baseline <- params$base
intervention <- params$intervention
start.year <- params$start.year
# 
# experiment <- 'default_config'
# baseline <- 'baseline'
# intervention <- '50All'
```

@@

base.path <- get_latest_runtime_subdirectory(here::here(out.path, baseline))
int.path <- get_latest_runtime_subdirectory(here::here(out.path, intervention))

base <- read.csv(paste0(base.path, 'qalys.csv'))
int <- read.csv(paste0(int.path, 'qalys.csv'))

# combine the dataframes
combined <- rbind(base, int)
```

@@

print(paste("There are", sum(is.na(combined.pop_boosted$pop_boosted)), "NA pop_boosted values in combined.pop.boosted.", sep = ' '))

@@

combined.diff <- combined %>%
  select(run_id, year, intervention, total_boost) %>%
  pivot_wider(names_from = 'intervention',
              values_from = 'total_boost') %>%
  mutate(diff.boost = .data[[intervention]] - .data[[baseline]])

ggplot(combined.diff, aes(x = year, y = diff.boost)) +
  geom_smooth() +
  labs(title = 'Total Boost amount by year') +
  scale_y_continuous(label = comma)

ggplot(combined, aes(x = year, y = alive_ratio, group = intervention, colour = intervention)) +
  geom_smooth() +
  labs(title = 'Ratio of living to dead in output dataframe')

## incidence of mortality
deaths <- combined %>%
  select(run_id, intervention, year, alive_pop, dead_pop) %>%
  group_by(run_id, intervention) %>%
  mutate(total_pop = alive_pop + dead_pop,
         deaths_this_year = dead_pop - lag(dead_pop)) %>%
  group_by(run_id, year, intervention) %>%
  summarise(death_incidence = deaths_this_year / total_pop)

ggplot(deaths, aes(x = year, y = death_incidence, group = intervention, colour = intervention)) +
  geom_smooth() +
  labs(title = 'Incidence of Mortality Comparison')
```

@@

```{r}
QALY_comparison(base = base,
                base.name = baseline,
                int = int,
                int.name = intervention)
```

@@

```{r}
sf12.plots(base = base,
           base.name = baseline,
           int = int,
           int.name = intervention)
```

@@

```{r}
auc.plots(base = base, 
          base.name = baseline,
          intervention = int,
          int.name = intervention)
```

@@

```{r}
cost.per.qaly(base = base,
              base.name = baseline,
              int = int,
              int.name = intervention,
              QALY_value = 70000,  # QALY value == £60,000
              int.label <- intervention)
```

@@

```{r}
ICER(base = base,
     base.name = baseline,
     int = int,
     int.name = intervention,
     QALY_value = 70000,
     int.label = intervention,
     start.year = start.year)
```

@@

```{r}
intervention.cost(base = base,
                  base.name = baseline,
                  int = int,
                  int.name = intervention,
                  int.label = intervention)
```

>>>>

```{r}
# experiment <- params$experiment
# baseline <- params$base
# intervention <- params$intervention
# #intervention2 <- params$intervention2
# start.year <- params$start.year
# # 
experiment <- 'glasgow_scaled'
baseline <- 'baseline'
ints <- c('50All', '50UniversalCredit')
start.year <- 2020
```

@@

expts <- c(baseline, ints)

combined <- data.frame()
for (expt in expts) {
  path <- get_latest_runtime_subdirectory(here::here(out.path, expt))
  data <- read.csv(paste0(path, 'qalys.csv'))
  combined <- rbind(combined, data)
}
```

```{r}
# # read in QALY files for baseline and interventions
# out.path <- here::here('output', experiment)
# 
# base.path <- get_latest_runtime_subdirectory(here::here(out.path, baseline))
# int.path <- get_latest_runtime_subdirectory(here::here(out.path, intervention1))
# 
# if (intervention2 != '') {
#   int2.path <- get_latest_runtime_subdirectory(here::here(out.path, intervention2))
# }
# 
# base <- read.csv(paste0(base.path, 'qalys.csv'))
# int <- read.csv(paste0(int.path, 'qalys.csv'))
# 
# # combine the dataframes
# combined <- rbind(base, int)
```

@@

# print(paste("There are", sum(is.na(combined.pop_boosted$pop_boosted)), "NA pop_boosted values in combined.pop.boosted.", sep = ' '))

@@

combined.diff <- combined %>%
  select(run_id, year, intervention, total_boost) %>%
  pivot_wider(names_from = 'intervention',
              values_from = 'total_boost') %>%
  mutate(across(all_of(ints), ~.x - .data[[baseline]], .names = "diff_{.col}")) %>%
  select(run_id, year, contains('diff_')) %>%
  pivot_longer(cols = contains('diff_'),
               names_prefix = 'diff_',
               names_to = 'scenario',
               values_to = 'total_boost')

ggplot(combined.diff, aes(x = year, y = total_boost, group = scenario, fill = scenario, color = scenario)) +
  geom_smooth() +
  labs(title = 'Total Boost amount by year') +
  scale_y_continuous(label = comma)
# 
# ggplot(combined, aes(x = year, y = alive_ratio, group = intervention, colour = intervention)) +
#   geom_smooth() +
#   labs(title = 'Ratio of living to dead in output dataframe')
# 
# ## incidence of mortality
# deaths <- combined %>%
#   select(run_id, intervention, year, alive_pop, dead_pop) %>%
#   group_by(run_id, intervention) %>%
#   mutate(total_pop = alive_pop + dead_pop,
#          deaths_this_year = dead_pop - lag(dead_pop)) %>%
#   group_by(run_id, year, intervention) %>%
#   summarise(death_incidence = deaths_this_year / total_pop)
# 
# ggplot(deaths, aes(x = year, y = death_incidence, group = intervention, colour = intervention)) +
#   geom_smooth() +
#   labs(title = 'Incidence of Mortality Comparison')
```

@@

```{r}
# QALY_comparison(base = base,
#                 base.name = baseline,
#                 int = int,
#                 int.name = intervention)

QALY_comparison(combined, ints)
```

@@

```{r}
sf12.plots(combined, ints)
```

@@

```{r}
auc.plots(combined, ints)
```

@@

```{r}
# cost.per.qaly(base = base,
#               base.name = baseline,
#               int = int,
#               int.name = intervention,
#               QALY_value = 70000,  # QALY value == £70,000
#               int.label <- intervention)
```

@@

```{r}
ICER(combined,
     ints,
     QALY_value = 70000,
     start.year = start.year)
```

@@

```{r}
# intervention.cost(base = base,
#                   base.name = baseline,
#                   int = int,
#                   int.name = intervention,
#                   int.label = intervention)
```
